The \project{unRAVE} catalog

### 2016-08-18 article/unrave.tex
woe is us

>>>>

We sought to construct a training set consisting of stars across the main-sequence,
sub-giant, and the red giant branch.  We require stars with precisely measured
effective temperature $\teff$, surface gravity $\logg$, and elemental abundances
of Fe, Mg, Si, Ti, Ca, Al, and Ni.  This proved to be difficult because the magnitude
range of \rave\ does not overlap substantially with high-resolution spectroscopic
surveys.  The fourth data release of the \project{Gaia-ESO} survey includes giant
and main-sequence stars, but only 142 overlap with \rave.  The most recent 
\project{APOGEE} data release \citep{apogee_dr13} reports labels for stars on the
giant branch and (uncalibrated values for) the main-sequence, but our tests indicated
that the main-sequence labels suffered from unexpected systematic effects.  A flat, 
then `up-turning' main-sequence is present, and the metallicity gradient trends in 
the opposite direction with respect to $\logg$ on the main-sequence (i.e., metal-poor
stars sit above the isochrones, not below).  If we move to lower-resolution studies,
there are 2,369 stars that overlap with \project{LAMOST} --- of which 2,213 have positive
S/N ratios in the $g$-band (\texttt{snrg}).  However, similar systematic effects are 
seen in the main-sequence, the labels are expectedly less precise given the lower
resolution, no detailed abundance information is available\footnote{Abundance 
information is available for \project{LAMOST} stars from \citet{Ho_2015}, but that 
sample contains only giant stars}, and there is only sparse sampling across the 
Hertsprung-Russell diagram.  The \project{GALAH} survey has a good overlap with \rave,
but results from that sample are not yet precise enough for our purposes.
